August 2025 Lipid Interactome Monthly Invoice

### 2025-08-29 BioinformaticsApplicationNote/Bioinformatics_ReviewerResponseLetter.qmd

Dear Dr. Hutchins,

We thank you again for the opportunity to address the reviewers' comments on our first draft of our manuscript -- we have included with this letter an updated mansucript draft and have incorporated as many of their suggestions as we could feasibly achieve in the Lipid Interactome site.

We are grateful for thought that the reviewers put into their comments. We interpreted several throughlines in their comments: 1. Requests for additional metadata about study methodology and the incorporation of additional data (e.g. accession numbers in addition to gene names), 2. Requests for additional information about data submission, processing, and harmonization methods, 3. Requests for an automated/scalable data submission pipeline, and 4. The identification of typographical errors, malformed links, and bugs in the site.

Many of these points have been addressed directly either in the text or on the Lipid Interactome repository. For example, the broken links and typographical errors in figure captions have been addressed, additional cell line information has been added to our *Comparing the Enriched Hits of Different Probes* Shiny app, we have included of accession number to convey crucial information about isoform identifications in addition to using gene name to identify hits (where possible in the original datasets; the authors of Hoglinger 2017 have been unresponsive and we do not have the accession number data for their results) and clarification about the qualitative nature of the comparisons displayed in the Shiny app. We have additionally provided links to download the R scripts which were used to "wrangle" the submitted data to the formats that our data visualization functions accept.

### 2025-08-29 HourlyTracking/202508_GG-Hours.qmd
updated hours sheet

---
titlJuly 2025 Lipid Interactome Monthly Invoice"
author: "Gaelen Guzman"
date: "2025 08 04"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 08 04}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

Carsten Schultz,

Please find below the hours I logged for the month of July 2025, with descriptions of each day's activity. In total, I performed 6 hours of work at an hourly rate of $50 (USD), for a total bill of $300.

@@

# Read the Hours.csv file and handle unnamed columns
hours_data <- read_csv(here("HourlyTracking/hours.csv"), col_names = c("Date", "Hours", "Activity"), show_col_types = FALSE) |>
  mutate(Date = as.Date(as.character(Date), format = "%Y%m%d")) |>
  select(Date, Hours, Activity) |>
  filter(Date >= as.Date("2025-07-01") & Date < as.Date("2025-08-01")) %>%  # Filter for April 2025
  glimpse()

>>>>

---
title: August 2025 Lipid Interactome Monthly Invoice
author: "Gaelen Guzman"
date: "2025 09 04"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 09 04}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

Dear Dr. Schultz,

Please find below the hours I logged for the month of August 2025, with descriptions of each day's activity. In total, I performed 4 hours of work at an hourly rate of $50 (USD), for a total bill of $200.

@@

# Read the Hours.csv file and handle unnamed columns
hours_data <- read_csv(here("HourlyTracking/hours.csv"), col_names = c("Date", "Hours", "Activity"), show_col_types = FALSE) |>
  mutate(Date = as.Date(as.character(Date), format = "%Y%m%d")) |>
  select(Date, Hours, Activity) |>
  filter(Date >= as.Date("2025-08-01") & Date < as.Date("2025-09-01")) %>%  # Filter for April 2025
  glimpse()
